Hydraulic bore interaction with a column - A comparison between the solution of the shallow equation and experimental results

### 2015-03-12 doc/paper/paper.tex
Started to add equation
add todo mark in paper.tex

\section{Dam Break with square column}\label{Sec:Square}
Figure \ref{fig:waveheight_square_x=11.0} gives a comparison of the time history of the wave height measured at $0.04m$ ahead of the leading edge of the square column($0.1m$ ahead of center of the column).
Note that this figure is from $t=3.0$ to $t=4.0$, which shows a shorter range compared to the previous figures.
There are two jumps in the result given by GeoClaw. A first jump with a change in water level from around $0.02$ to $0.1$ and a second jump from $0.1$ to a higher level of around $0.22$.
If we recall from Figure \ref{fig:waveheight_nocolumn} that the wave height is around $0.1$, we can confirm that this first jump is caused by the shock wave originate in the dambreak. The second jump represents the wave reflected by the column.  
If we compare the time interval from the first to the second jump between measurement location $x=11.0$ in Figure \ref{fig:waveheight_square_x=11.0} and location $11.02$ in Figure \ref{fig:waveheight_square_x=11.02} we can see that as we get closer to the column, this time interval gets shorter.
There are two distinct differences between the GeoClaw and the experimental results. First, in the experiment, the dambreak causes a smooth increase in water height. Second, the arrival time of the peak predicted by GeoClaw is about $0.08$ seconds ahead of the time measured in the experiment.  

@@

If we zoom in Figure \ref{fig:waveheight_nocolumn} for smaller time range from $t=3s$ to $t=4s$, we get Figure \ref{fig:waveheight_nocolumn_zoomin}.
In Figure \ref{fig:waveheight_nocolumn_zoomin}, arrival time of peak predicted by geoclaw is almost the same as that from experiment (only about 0.02 second earlier).  

>>>>

\section{Dam Break with square column}\label{Sec:Square}
Figure \ref{fig:waveheight_square_x=11.0} gives a comparison of the time history of the wave height measured at $0.04m$ ahead of the leading edge of the square column($0.1m$ ahead of center of the column).
Note that this figure is from $t=3.0$ to $t=4.0$, which shows a shorter range compared to the previous figures.
There are two jumps in the result given by GeoClaw. A first jump with a change in water level from around $0.02$ to $0.1$ and a second jump from $0.1$ to a higher level of around $0.22$.
If we recall from Figure \ref{fig:waveheight_nocolumn} that the wave height is around $0.1$, we can confirm that this first jump is caused by the shock wave originate in the dambreak. The second jump represents the wave reflected by the column.  
If we compare the time interval from the first to the second jump between measurement location $x=11.0$ in Figure \ref{fig:waveheight_square_x=11.0} and location $11.02$ in Figure \ref{fig:waveheight_square_x=11.02} we can see that as we get closer to the column, this time interval gets shorter.
\par
There are two distinct differences between the GeoClaw and the experimental results. First, in the experiment, the dambreak causes a smooth increase in water height. Second, the arrival time of the peak predicted by GeoClaw is about $0.08$ seconds ahead of the time measured in the experiment.  
\par

%todo

@@

%todo
%If we zoom in Figure \ref{fig:waveheight_nocolumn} for smaller time range from $t=3s$ to $t=4s$, we get Figure \ref{fig:waveheight_nocolumn_zoomin}.
%In Figure \ref{fig:waveheight_nocolumn_zoomin}, arrival time of peak predicted by geoclaw is almost the same as that from experiment (only about 0.02 second earlier).  
